An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-09 gas-adsorption/rsc-gas-ads-complete.tex
we dont look at any 'ol condition
mason is all we need to cite for that; both numbers from there

In this work, we place a rigorous upper bound on the isothermal deliverable capacity of a
pure gas in a rigid substrate by endowing a control volume with a spatially
uniform background energy field. Instead of using a molecular model for the
gas~\cite{gomez2017impact}, we use the experimental equation of state to
account for gas-gas interactions. In addition, we prove using the calculus of
variations that this spatially uniform substrate yields a maximal deliverable
capacity. We use our framework to place an upper bound on the deliverable
capacity of methane and hydrogen gas.

@@

\section{Flexible two-phase model}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{methane-298-flexible}
    \caption{Maximal possible deliverable capacity of methane in a two-phase, collapsing substrate at 298\ K as a function of the free energy difference 
      between open and closed phases. The experimental deliverable capacity for Co(bdp) is shown for
       comparison~\cite{mason2015methane}, along with the free energy difference between open and closed conformations~\cite{mason2015methane, choi2008broadly}.}
    \label{fig:methane-flexible}
\end{figure}
Although our deliverable capacity limit does not directly apply to materials that change conformation in
response to gas adsorption, we can estimate enhancements in the deliverable capacity provided by
such materials. 
For example, consider a material such as Co(bdp) \cite{mason2015methane} that 
can, actuated by the presence of gas, switch between two distinct structural phases: 
an ``open'' phase where gas molecules can fit in the pore space and a 
collapsed, ``closed'' phase in which no gas can fit inside.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-298-flexible}
    \caption{Deliverable capacity of hydrogen in a flexible substrate at 298\ K as a function of the free energy difference 
      between open and closed phases.}
    \label{fig:hydrogen-flexible}
\end{figure}

>>>>

In this work, we place a rigorous upper bound on the isothermal deliverable capacity of a
pure gas in a rigid substrate by endowing a control volume with a spatially
uniform background energy field. Instead of using a molecular model for the
gas~\cite{gomez2017impact}, we use the experimental equation of state to
account for gas-gas interactions. In addition, we prove using the calculus of
variations that this spatially uniform substrate yields a maximal deliverable
capacity. We use our framework to place an upper bound on the deliverable
capacity of methane and hydrogen gas at conditions relevant to vehicular storage.

@@

\section{Flexible two-phase model}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{methane-298-flexible}
    \caption{Maximal possible deliverable capacity of methane in a two-phase, collapsing substrate at 298\ K as a function of the free energy difference 
      between open and closed phases. The experimental deliverable capacity for Co(bdp) is shown for
       comparison, along with the free energy difference between open and closed conformations~\cite{mason2015methane}.}
    \label{fig:methane-flexible}
\end{figure}
Although our deliverable capacity limit does not directly apply to materials that change conformation in
response to gas adsorption, we can estimate enhancements in the deliverable capacity provided by
such materials. 
For example, consider a material such as Co(bdp) \cite{mason2015methane} that 
can, actuated by the presence of gas, switch between two distinct structural phases: 
an ``open'' phase where gas molecules can fit in the pore space and a 
collapsed, ``closed'' phase in which no gas can fit inside.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-298-flexible}
    \caption{Deliverable capacity of hydrogen in a flexible, two-phase substrate at 298\ K as a function of the free energy difference 
      between open and closed phases.}
    \label{fig:hydrogen-flexible}
\end{figure}
